Evolved disk population of young brown dwarfs in \emph{Ophiuchus}\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2015-04-06 chIMACS/ms.tex
diss now includes IMACS chapter at v0.4

\chapter{Evolved disk population of young brown dwarfs in \emph{Ophiuchus}\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}}

\begin{document}
\maketitle

@@

\input{chIMACS/tables/tbl_photomCatalog}

@@

\input{chIMACS/tables/tbl_selectionScores.tex}

@@

\input{chIMACS/tables/tbl_scoring2Priority.tex}

@@

\input{chIMACS/tables/tbl_IMACSslitMasks.tex}

@@

\begin{landscape}
	\input{chIMACS/tables/tbl_members_phot_deluxe.tex}
\end{landscape}

@@

\begin{landscape}
	\input{chIMACS/tables/tbl_members_physics_deluxe.tex}
\end{landscape}

@@

\end{document}

>>>>

\chapter{Evolved disk population of young brown dwarfs in \emph{Ophiuchus}}

@@

%\input{chIMACS/tables/tbl_photomCatalog}

@@

%\input{chIMACS/tables/tbl_selectionScores.tex}

@@

%\input{chIMACS/tables/tbl_scoring2Priority.tex}

@@

%\input{chIMACS/tables/tbl_IMACSslitMasks.tex}

@@

%\begin{landscape}
%	\input{chIMACS/tables/tbl_members_phot_deluxe.tex}
%\end{landscape}

@@

%\begin{landscape}
%	\input{chIMACS/tables/tbl_members_physics_deluxe.tex}
%\end{landscape}

@@
